Universal algebra and the \texorpdfstring{$ \lambda $}{lambda}-calculus

### 2024-06-14 report/src/paper.tex
Prettify the proofs that the pullback is full, and that epsilon_B is an isomorphism of E_{R_A}(U)-algebras

\begin{lemma}
  The pullback functor
  \[ [a \mapsto \epsilon_A^{-1}(a) \bullet_{E_{\R_A}(U)} (), \iota_{\Lambda_n}]_n^* \]
  is essentially surjective.
\end{lemma}
\begin{proof}
  Take $ B : \Alg{\Lambda_A} $. By Lemma \ref{lem:extensions-algebra-coslice} we can consider $ B $ to be a object in the coslice category $ h : \Alg{\Lambda}(A, B) $. As shown in Section \ref{sec:elementary-fundamental-theorem}, $ h $ sends elements in $ \R_A(U^n, U) $ to elements in $ \R_B(U^n, U) $, so we can regard it as a morphism $ h: \AlgTh(E_{\R_A}(U), E_{\R_B}(U)) $. We then have a $ E_{\R_A}(U) $-algebra $ h^*(E_{\R_B}(U)_0) $. Now we need to prove that we have an isomorphism of $ \Lambda_A $-algebras
  \[ ([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \cdot h)^*(E_{\R_B}(U)_0) \cong B. \]
  Under the equivalence in Lemma \ref{lem:extensions-algebra-coslice}, this pullback of $ E_{\R_B}(U)_0 $ corresponds to some $ (B^\prime, h^\prime) : (A \downarrow \Alg \Lambda) $. The set of $ B^\prime $ is $ \R_B(I, U) $, its $ \Lambda $-action is given by
  \[ (f, b) \mapsto h(\iota_{\Lambda_n}(f)) \bullet_{E_{\R_B}(U)} b, \]
  and the morphism $ h^\prime $ is given by $ h^\prime(a) = h(\epsilon_A^{-1}(a)) $. Note that by initiality of $ \Lambda $, the following diagram of algebraic theories commutes
  \begin{center}
    \begin{tikzcd}
      & \Lambda \arrow[ld, "\iota_\Lambda"'] \arrow[rd, "\iota_\Lambda"]\\
      E_{\R_A}(U) \arrow[rr, "h"] && E_{\R_B}(U)
    \end{tikzcd}
  \end{center}
  Therefore, $ h_n(\iota_{\Lambda_n}(f)) = \iota_{\Lambda_n}(f) $, so $ B^\prime = \iota_\Lambda^*(E_{\R_B}(U)_0) $. We have the following diagram in $ \Alg \Lambda $:
  \begin{center}
    \begin{tikzcd}[sep = large]
      & A \arrow[ld, "a \mapsto h(\epsilon_A^{-1}(a))"'] \arrow[rd, "h"]\\
      E_{\R_B}(U)_0 \arrow[rr, "\epsilon_B"] & & B
    \end{tikzcd}
  \end{center}
  \TODO: Show commutativity

  which shows that $ \epsilon_B $ is an isomorphism in the coslice category under $ A $. Pulling this isomorphism back along the equivalence from Lemma \ref{lem:extensions-algebra-coslice} gives an isomorphism of $ \Lambda_A $-algebras
  \[ ([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \cdot h)^*(E_{\R_B}(U)_0) \cong B \]
  and this concludes the proof.
\end{proof}

\begin{lemma}
  For $ \iota_\Lambda: \LamTh(\Lambda, E_{\R_A}(U)) $ and $ s_i : \Lambda_n $, we have
  \[ \iota_\Lambda((s_i)_i) = \langle x_i \rangle_i \bullet_A (\iota_\Lambda(s_i))_i, \]
  and we will call the latter $ \langle \iota_\Lambda(s_i) \rangle_i $.
\end{lemma}
\begin{proof}
  By the recursive nature of the definitions of $ (s_i)_i $ and $ \langle a_i \rangle_i $, it suffices to show that for $ a, b : \Lambda_n $, $ \iota_\Lambda((a, b)) = \langle \iota_\Lambda(a), \iota_\Lambda(b) \rangle $ and that $ \iota_\Lambda(c_n) = I_c $. Since $ \iota_\Lambda $ is defined via structural induction, this is just a matter of straightforward but tedious unfolding and rewriting, at some point using the fact that $ \iota_\Lambda(a) \circ U^n = \iota_\Lambda(a) $:
  \begin{align*}
    \iota_\Lambda((a, b))
    &= \iota_\Lambda(\lambda x_{n + 1}, x_{n + 1} \iota_{n, n + 1}(a) \iota_{n, n + 1}(b))\\
    &= (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet_A \iota_\Lambda(x_{n + 1} \iota_{n, n + 1}(a) \iota_{n, n + 1}(b))\\
    &= (\lambda x_4 x_5, (\lambda x_6, x_1 x_6 (x_2 x_6) (x_3 x_6)) (x_4, x_5)) \bullet_A (\iota_\Lambda(x_{n + 1}), \iota_\Lambda(a \bullet_\Lambda (x_{n + 1, i})_i), \iota_\Lambda(b \bullet_\Lambda (x_{n + 1, i})_i))\\
    &= (\lambda x_3 x_4, \pi_{n + 1, n + 1} (x_3, x_4) ((x_1 \circ \langle \pi_{n + 1, i} \rangle)_i (x_3, x_4)) ((x_2 \circ \langle \pi_{n + 1, i} \rangle)_i (x_3, x_4))) \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))\\
    &= (\lambda x_3 x_4, x_4 ((x_1 \circ \langle \pi_{n, i} \rangle_i) x_3) ((x_2 \circ \langle \pi_{n, i} \rangle_i) x_3)) \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))\\
    &= (\lambda x_3 x_4, x_4 (x_1 x_3) (x_2 x_3)) \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))\\
    &= \langle x_1, x_2 \rangle \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))
  \end{align*}
  and
  \begin{align*}
    \iota_\Lambda(c_n)
    &= \iota_\Lambda(\lambda x_{n + 1}, x_{n + 1})\\
    &= (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet_A \iota_\Lambda(x_{n + 1})\\
    &= \lambda x_1 x_2, \pi_{n + 1, n + 1} (x_1, x_2)\\
    &= \lambda x_1 x_2, x_2\\
    &= I_c.
  \end{align*}
\end{proof}

\begin{remark}\label{rem:endomorphism-theory-algebra-to-endomorphism-theory-algebra}
  Note that for any $ E_{\R_A}(U) $-algebra $ B $, we can view the pullback $ \Lambda_A $-algebra $ [a \mapsto \epsilon_A^{-1}(a) \bullet_{E_{\R_A}(U)} (), \iota_{\Lambda_n}]^* B $ as an object in the coslice category under $ A $, given by
  \[ a \mapsto \epsilon_A^{-1}(a) \bullet_B () : \Alg \Lambda(A, \iota_\Lambda^* B). \]
  Functoriality of the endomorphism theory construction of the respective categories of retracts, gives a $ \lambda $-theory morphism
  \[ a \mapsto \epsilon_A^{-1}(a) \bullet_B (): \LamTh(E_{\R_A}(U), E_{\R_{\iota_\Lambda^* B}}(U)). \]
  Then, we can pull back the theory algebra along this morphism, to get, again a $ E_{\R_A}(U) $-algebra
  \[ (a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* (E_{\R_{\iota_\Lambda^* B}}(U)_0). \]
\end{remark}

\begin{lemma}
  For $ B : \Alg {E_{\R_A}(U)} $, we have an isomorphism of $ E_{\R_A}(U) $-algebras given by
  \[ \epsilon_{\iota_\Lambda^* B} : (a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* (E_{\R_{\iota_\Lambda^* B}}(U)_0) \xrightarrow \sim B. \]
\end{lemma}
\begin{proof}
  Note that the underlying set of $ (a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* (E_{\R_{\iota_\Lambda^* B}}(U)_0) $ is $ \R_{\iota_\Lambda^* B}(I, U) $, and that $ \epsilon_{\iota_\Lambda^* B} $ is a bijection between this set and $ B $. Now we only need to show that it is a morphism of $ E_{\R_A}(U) $-algebras. Take $ s: E_{\R_A}(U)_n $ and all $ b : E_{\R_{\iota_\Lambda^* B}}(U)_0^n $. We have
  \begin{align*}
    \epsilon_{\iota_\Lambda^* B}(s \bullet_{(a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* E_{\R_{\iota_\Lambda^* B}}(U)_0} b)
    &= \iota_\Lambda(x_1 c_1) \bullet_B (s \bullet_{(a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* E_{\R_{\iota_\Lambda^* B}}(U)_0} b)\\
    &= \iota_\Lambda(x_1 c_1) \bullet_B ((\epsilon_A^{-1}(s) \bullet_B ()) \bullet_{E_{\R_{\iota_\Lambda^* B}}(U)_0} b)\\
    &= \iota_\Lambda(x_1 c_1) \bullet_B (\iota_\Lambda(x_1 \circ \langle x_2, \dots, x_{n + 1} \rangle) \bullet_B (\epsilon_A^{-1}(s) \bullet_B (), b_1, \dots, b_n))\\
    &= \iota_\Lambda(x_1 c_1) \bullet_B ((\iota_\Lambda(x_1 \circ \langle x_{i + 1} \rangle_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n))) \bullet_B b)\\
    &= (\iota_\Lambda(x_1 c_1) \bullet_{E_{\R_A}(U)} (\iota_\Lambda(x_1 \circ \langle x_{i + 1} \rangle_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n)))) \bullet_B b\\
    &= (\iota_\Lambda(x_1 (x_{i + 1} c_{n + 1})_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n))) \bullet_B b\\
    &= (\iota_\Lambda(x_1 (x_{i + 1} c_{n + 1})_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n))) \bullet_B b\\
    &= (\epsilon_A^{-1}(s) (x_i c_n)_i) \bullet_B b\\
    &= (\epsilon_A^{-1}(s) (x_i)_i \bullet \iota_\Lambda(x_i c_n)_i) \bullet_B b.
  \end{align*}
  Also,
  \begin{align*}
    s \bullet_B (\epsilon_B(b_i))_i
    &= s \bullet_B (\iota_\Lambda(x_1 c_1) \bullet_B b_i)_i\\
    &= s \bullet_B (\iota_\Lambda(x_i c_n) \bullet_B (b_j)_j)_i\\
    &= (s \bullet_{E_{\R_A}(U)} (\iota_\Lambda(x_i c_n))_i) \bullet_B b.
  \end{align*}
  Then the result follows from the fact that
  \begin{align*}
    ((\epsilon_A^{-1}(s)) \bullet_{E_{\R_A}(U)} ()) (x_i)_i
    &= ((\lambda x_2, x_1) \bullet_A s) (x_i)_i\\
    &= (\lambda x_3, x_1 x_3 x_2 x_3) \bullet_A ((\lambda x_2, x_1) \bullet_A s, \iota_\Lambda((x_i)_i))\\
    &= (\lambda x_3, x_1 x_2 x_3) \bullet_A (s, \langle \iota_\Lambda(x_i) \rangle_i)\\
    &= (x_1 \circ x_2) \bullet_A (s, U^n)\\
    &= s.
  \end{align*}
\end{proof}

>>>>

\begin{lemma}
  The isomorphisms $ \epsilon_A : E_{\R_A}(U)_0 \xrightarrow \sim A $ form a natural transformation. That is, for all $ h: \Alg \Lambda(A, B) $, the following diagram commutes:
  \begin{center}
    \begin{tikzcd}
      E_{\R_A}(U)_0 \arrow[r, "h"] \arrow[d, "\epsilon_A"] & E_{\R_B}(U)_0 \arrow[d, "\epsilon_B"]\\
      A \arrow[r, "h"] & B
    \end{tikzcd}
  \end{center}
\end{lemma}
\begin{proof}
  This follows from simple unfolding and using the property of algebra morphisms: For all $ f: E_{\R_A}(U)_0 = \{ f : A \mid (x_1 \circ I_c) \bullet_A f = f \} $,
  \begin{align*}
    \epsilon_B(h(f))
    &= (x_1 c_1) \bullet_B h(f)\\
    &= h((x_1 c_1) \bullet_A f)\\
    &= h(\epsilon_A(f)).
  \end{align*}
\end{proof}

\begin{lemma}
  The pullback functor
  \[ [a \mapsto \epsilon_A^{-1}(a) \bullet_{E_{\R_A}(U)} (), \iota_{\Lambda_n}]_n^* \]
  is essentially surjective.
\end{lemma}
\begin{proof}
  Take $ B : \Alg{\Lambda_A} $. By Lemma \ref{lem:extensions-algebra-coslice} we can consider $ B $ to be a object in the coslice category $ h : \Alg{\Lambda}(A, B) $. As shown in Section \ref{sec:elementary-fundamental-theorem}, $ h $ sends elements in $ \R_A(U^n, U) $ to elements in $ \R_B(U^n, U) $, so we can regard it as a morphism $ (h)_n: \AlgTh(E_{\R_A}(U), E_{\R_B}(U)) $. We then have a $ E_{\R_A}(U) $-algebra $ (h)_n^*(E_{\R_B}(U)_0) $. Now we need to prove that we have an isomorphism of $ \Lambda_A $-algebras
  \[ ([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \cdot (h)_n)^*(E_{\R_B}(U)_0) \cong B. \]
  Under the equivalence in Lemma \ref{lem:extensions-algebra-coslice}, this pullback of $ E_{\R_B}(U)_0 $ corresponds to some $ (B^\prime, h^\prime) : (A \downarrow \Alg \Lambda) $. The set of $ B^\prime $ is $ \R_B(I, U) $, its $ \Lambda $-action is given by
  \[ (f, b) \mapsto h(\iota_{\Lambda_n}(f)) \bullet_{E_{\R_B}(U)} b, \]
  and the morphism $ h^\prime $ is given by $ h^\prime(a) = h(\epsilon_A^{-1}(a)) $. Note that by initiality of $ \Lambda $, the following diagram of algebraic theories commutes
  \begin{center}
    \begin{tikzcd}
      & \Lambda \arrow[ld, "\iota_\Lambda"'] \arrow[rd, "\iota_\Lambda"]\\
      E_{\R_A}(U) \arrow[rr, "(h)_n"] && E_{\R_B}(U)
    \end{tikzcd}
  \end{center}
  Therefore, $ h(\iota_{\Lambda_n}(f)) = \iota_{\Lambda_n}(f) $, so the $ \Lambda $-action on $ B^\prime $ is exactly the action on $ \iota_\Lambda^*(E_{\R_B}(U)_0) $, which means that $ B^\prime = \iota_\Lambda^*(E_{\R_B}(U)_0) $. We have the following diagram in $ \Alg \Lambda $:
  \begin{center}
    \begin{tikzcd}[sep = large]
      & A \arrow[ld, "a \mapsto h(\epsilon_A^{-1}(a))"'] \arrow[rd, "h"]\\
      E_{\R_B}(U)_0 \arrow[rr, "\epsilon_B", "\sim"'] & & B
    \end{tikzcd}
  \end{center}
  By naturality of $ \epsilon $, this diagram commutes, which shows that $ \epsilon_B $ is an isomorphism in the coslice category under $ A $. Pulling this isomorphism back along the equivalence from Lemma \ref{lem:extensions-algebra-coslice} gives an isomorphism of $ \Lambda_A $-algebras
  \[ ([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \cdot h)^*(E_{\R_B}(U)_0) \cong B \]
  and this concludes the proof.
\end{proof}

\begin{lemma}
  For $ \iota_\Lambda: \LamTh(\Lambda, E_{\R_A}(U)) $ and $ s_i : \Lambda_n $, we have
  \[ \iota_\Lambda((s_i)_i) = \langle x_i \rangle_i \bullet_A (\iota_\Lambda(s_i))_i. \]
\end{lemma}
\begin{proof}
  By the recursive nature of the definitions of $ (s_i)_i $ and $ \langle x_i \rangle_i $, it suffices to show that for $ a, b : \Lambda_n $, $ \iota_\Lambda((a, b)) = \langle x_1, x_2 \rangle \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b)) $ and that $ \iota_\Lambda(c_n) = I_c \bullet () $. Since $ \iota_\Lambda $ is defined via structural induction, this is just a matter of straightforward but tedious unfolding and rewriting, at some point using the fact that $ (x_1 \circ U^n) \bullet_A \iota_\Lambda(a) = \iota_\Lambda(a) $:
  \begin{align*}
    \iota_\Lambda((a, b))
    &= \iota_\Lambda(\lambda x_{n + 1}, x_{n + 1} \iota_{n, n + 1}(a) \iota_{n, n + 1}(b))\\
    &= (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet_A \iota_\Lambda(x_{n + 1} \iota_{n, n + 1}(a) \iota_{n, n + 1}(b))\\
    &= (\lambda x_4 x_5, (\lambda x_6, x_1 x_6 (x_2 x_6) (x_3 x_6)) (x_4, x_5)) \bullet_A (\iota_\Lambda(x_{n + 1}), \iota_\Lambda(a \bullet_\Lambda (x_{n + 1, i})_i), \iota_\Lambda(b \bullet_\Lambda (x_{n + 1, i})_i))\\
    &= (\lambda x_3 x_4, \pi_{n + 1, n + 1} (x_3, x_4) ((x_1 \circ \langle \pi_{n + 1, i} \rangle)_i (x_3, x_4)) ((x_2 \circ \langle \pi_{n + 1, i} \rangle)_i (x_3, x_4))) \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))\\
    &= (\lambda x_3 x_4, x_4 ((x_1 \circ \langle \pi_{n, i} \rangle_i) x_3) ((x_2 \circ \langle \pi_{n, i} \rangle_i) x_3)) \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))\\
    &= (\lambda x_3 x_4, x_4 (x_1 x_3) (x_2 x_3)) \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))\\
    &= \langle x_1, x_2 \rangle \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))
  \end{align*}
  and
  \begin{align*}
    \iota_\Lambda(c_n)
    &= \iota_\Lambda(\lambda x_{n + 1}, x_{n + 1})\\
    &= (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet_A \iota_\Lambda(x_{n + 1})\\
    &= (\lambda x_1 x_2, \pi_{n + 1, n + 1} (x_1, x_2)) \bullet_A ()\\
    &= (\lambda x_1 x_2, x_2) \bullet_A ()\\
    &= I_c \bullet_A ().
  \end{align*}
\end{proof}

\begin{remark}\label{rem:endomorphism-theory-algebra-to-endomorphism-theory-algebra}
  Note that for any $ E_{\R_A}(U) $-algebra $ B $, we can view the pullback $ \Lambda_A $-algebra $ [a \mapsto \epsilon_A^{-1}(a) \bullet_{E_{\R_A}(U)} (), \iota_{\Lambda_n}]^* B $ as an object in the coslice category under $ A $, given by
  \[ a \mapsto \epsilon_A^{-1}(a) \bullet_B () : \Alg \Lambda(A, \iota_\Lambda^* B). \]
  Functoriality of the endomorphism theory construction of $ U : \R_A $ and $ U : \R_{\iota_\Lambda^* B} $, gives a $ \lambda $-theory morphism
  \[ a \mapsto \epsilon_A^{-1}(a) \bullet_B (): \LamTh(E_{\R_A}(U), E_{\R_{\iota_\Lambda^* B}}(U)). \]
  Then, we can pull back the theory algebra along this morphism, to get, again a $ E_{\R_A}(U) $-algebra
  \[ (a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* (E_{\R_{\iota_\Lambda^* B}}(U)_0). \]
\end{remark}

\begin{lemma}
  For $ B : \Alg {E_{\R_A}(U)} $, we have an isomorphism of $ E_{\R_A}(U) $-algebras given by
  \[ \epsilon_{\iota_\Lambda^* B} : (a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* (E_{\R_{\iota_\Lambda^* B}}(U)_0) \xrightarrow \sim B. \]
\end{lemma}
\begin{proof}
  Note that the underlying set of $ (a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* (E_{\R_{\iota_\Lambda^* B}}(U)_0) $ is $ \R_{\iota_\Lambda^* B}(I, U) $, and that $ \epsilon_{\iota_\Lambda^* B} $ is a bijection between this set and $ B $. Now we only need to show that it is a morphism of $ E_{\R_A}(U) $-algebras. Take $ s: E_{\R_A}(U)_n $ and all $ b : E_{\R_{\iota_\Lambda^* B}}(U)_0^n $. We have
  \begin{align*}
    \epsilon_{\iota_\Lambda^* B}(s \bullet b)
    &= \iota_\Lambda(x_1 c_1) \bullet_B ((\epsilon_A^{-1}(s) \bullet_B ()) \bullet_{E_{\R_{\iota_\Lambda^* B}}(U)_0} b)\\
    &= \iota_\Lambda(x_1 c_1) \bullet_B (\iota_\Lambda(x_1 \circ \langle x_2, \dots, x_{n + 1} \rangle) \bullet_B (\epsilon_A^{-1}(s) \bullet_B (), b_1, \dots, b_n))\\
    &= \iota_\Lambda(x_1 c_1) \bullet_B ((\iota_\Lambda(x_1 \circ \langle x_{i + 1} \rangle_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n))) \bullet_B b)\\
    &= (\iota_\Lambda(x_1 c_1) \bullet_{E_{\R_A}(U)} (\iota_\Lambda(x_1 \circ \langle x_{i + 1} \rangle_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n)))) \bullet_B b\\
    &= (\iota_\Lambda(x_1 (x_{i + 1} c_{n + 1})_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n))) \bullet_B b\\
    &= (\iota_\Lambda(x_1 x_2) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda((x_i c_n)_i))) \bullet_B b\\
    &= ((\iota_\Lambda(x_1 x_2) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda((x_i)_i))) \bullet_{E_{\R_A}(U)} (x_i c_n)_i) \bullet_B b\\
  \end{align*}
  Also,
  \begin{align*}
    s \bullet_B (\epsilon_B(b_i))_i
    &= s \bullet_B (\iota_\Lambda(x_1 c_1) \bullet_B b_i)_i\\
    &= s \bullet_B (\iota_\Lambda(x_i c_n) \bullet_B (b_j)_j)_i\\
    &= (s \bullet_{E_{\R_A}(U)} (\iota_\Lambda(x_i c_n))_i) \bullet_B b.
  \end{align*}
  Then the result follows from the fact that
  \begin{align*}
    \iota_\Lambda(x_1 x_2) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda((x_i)_i))
    &= \iota_\Lambda(x_1 x_2) \bullet_{E_{\R_A}(U)} ((\lambda x_2, x_1) \bullet_A s, \langle x_i \rangle_i \bullet_A (\iota_\Lambda(x_i))_i)\\
    &= (\lambda x_3, x_1 x_3 x_2 x_3) \bullet_A ((\lambda x_2, x_1) \bullet_A s, \langle x_i \rangle_i \bullet_A (\pi_{n, i} \bullet_A ())_i)\\
    &= (\lambda x_3, x_1 x_2 x_3) \bullet_A (s, \langle \pi_{n, i} \rangle_i \bullet_A ())\\
    &= (x_1 \circ x_2) \bullet_A (s, U^n \bullet_A ())\\
    &= s.
  \end{align*}
\end{proof}
